Thesis outline

### 2017-07-19 KellyDouglass/Thesis/preamble.tex
Added figures for small-scale and GV to presentation; minor changes to Thesis
Updated text in small scale environment chapter

\begin{DUTdedications}
\begin{center}
To my parents\\
You told me to reach for the stars\\
Will galaxies do?
\end{center}
\end{DUTdedications}

@@

% Family
Of course, none of this would be possible without the infinite love and support 
from my family.  Thank you Dad, Mom, Kelly, and Ren\'{e}e for always pushing me 
to work my hardest and do my best.  Thank you for challenging me in so many 
ways.  I love you guys, and I it means so much that you are here today!

>>>>

\begin{DUTdedications}
\begin{center}
To my parents\\
You always encouraged me to reach for the stars\\
Will galaxies do?
\end{center}
\end{DUTdedications}

@@

% Family
Of course, none of this would be possible without the infinite love and support 
from my family.  Thank you Dad, Mom, Kelly, and Ren\'{e}e for always pushing me 
to work my hardest and do my best.  Thank you for challenging me in so many 
ways.  I love you guys, and it means so much that you are here today!
